Determinism, Complexity, and Predictability in Computer Performance

### 2014-02-26 pecomplexity.tex
titles and notes
adding related works and edits to intro
major edits on the results section
Also some diddling in other sections to get cross refs to work, and to
put the table in an appendix

\documentclass{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parIEEEabrvskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{amsthm}

@@

\newtheorem*{mydef}{Definition}
\title{Determinism, Complexity, and Predictability in Computer Performance\\
Quantifying structured complexity and its role in predictability: With applications to predicting computer performance.
\\ Quantifying Predictability through Structural Complexity
\\ Quantifying Predictability using Structural Complexity
}

@@

>>>>

\documentclass{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parIEEEabrvskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{color}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{amsthm}

@@

\newtheorem*{mydef}{Definition}
\title{Determinism, Complexity, and Predictability in Computer Performance\\
Quantifying structured complexity and its role in predictability: With applications to predicting computer performance.
\\ {\color{green}Quantifying Predictability through Structural Complexity}
\\ Quantifying Predictability using Structural Complexity 
\\Decoding Predictability in Complicated Real-Valued Time Series: The balance between complexity and temporal structure
\\Decoding Complicated Time Series: The balance between complexity and temporal structure and the implications for predictability
}

@@

\section{Appendix}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
                   & MASE LMA    & MASE ARIMA &MASE na\"{i}ve   & $l=6$ \\
\hline
\gcc                  & $ 1.5296\pm 0.0214$ & $1.8366 \pm0.0157 $ & $0.9510 \pm 0.0011$ & $0.9430 \pm 0.0013$ \\

\col           & $ 0.0500 \pm0.0018  $ & $0.5989  \pm 0.2114 $ & $0.5707\pm0.0017$&  $0.5131 \pm 0.0034$ \\

\svdone     & $ 0.8273\pm 0.0755$ & $ 0.7141\pm 0.0745 $ & $2.6763\pm4.3282$&  $0.9572 \pm 0.0156$ \\
\svdtwo     & $1.2789 \pm0.0196 $ & $2.1626 \pm0.0265 $ &  $3.0543\pm0.0404$ &   $0.8464 \pm0.0044$ \\
\svdthree       & $0.6192 \pm0.0209 $ & $0.7129 \pm 0.0096 $ & $31.3857\pm 0.2820$ &  $0.7157 \pm 0.0056$ \\
\svdfour     & $ 0.7789\pm0.0358 $ & $0.9787 \pm0.0321 $ & $2.6613\pm0.0739$ & $0.8246 \pm 0.0077$ \\
\svdfive     & $ 0.7177\pm 0.0483 $ & $2.3700  \pm 0.0505 $ & $20.8703 \pm 0.1915$&  $0.6776 \pm 0.0068$ \\
\svdsix     & $ 0.7393\pm 0.0682 $ & $ 1.4379\pm 0.0609$ & $2.1967\pm0.0830$&  $0.7475 \pm 0.0106$ \\
\hline
\end{tabular}
\end{center}
\caption{Detailed MASE scores}
\label{tab:error}
\end{table}%
